Interisland movements of woodland caribou in Newfoundland

### 2020-02-21 paper/manuscript.Rmd
P3

The Fogo Island archipelago, off the coast of Newfoundland, Canada (49°N, 54°W),
is home to approximately 300 woodland caribou. During routine fieldwork on May
30, 2017, we observed an unmarked adult male caribou swim between Perry and
Eastern Indian Islands (Figure 1), a swim of at least 470 m which took ~9
minutes (~52 m per minute). This observation prompted us to investigate whether
GPS radio-collared caribou in the population (n = 29 adult females) also swam
between islands. Using these remotely sensed relocations, we determined that
this observation was not unique and that several individuals engaged in this
behaviour (details below).
<!--Is it better to just state our results here, or give this sort of teaser? Initially I had "86 events by 3 individuals" here, but then we ignore that for a couple paragraphs of context before getting back into it... which seemed weird-->

@@

We identified swimming events as two consecutive GPS locations from an
individual on different islands. This region typically experiences pack ice
during the winter, so caribou may be able to travel between islands by
walking over the ice. We restricted our GPS data to the ice-free period of the
year (April 1 - November 25) to avoid this possibility. Using these criteria, we
identified three adult female caribou that collectively engaged in 86 swimming
events (Figure 2).

>>>>

The Fogo Island archipelago, off the coast of Newfoundland, Canada (49°N, 54°W),
is home to approximately 300 woodland caribou. During routine fieldwork on May
30, 2017, we observed an unmarked adult male caribou swim between Perry and
Eastern Indian Islands (Figure 1), a swim of at least 470 m which took ~9
minutes (~52 m per minute). This observation prompted us to investigate whether swimming behaviour was common among GPS radio-collared caribou (n = 29 adult females) in the population. We identified swimming events as two consecutive GPS locations from an
individual on different islands. This region typically experiences pack ice
during the winter, so caribou may be able to travel between islands by
walking over the ice. We restricted our GPS data to the ice-free period of the
year (April 1 - November 25) to avoid this possibility. Using these criteria, we
identified three adult female caribou that collectively engaged in 86 swimming
events (Figure 2).
<!--Is it better to just state our results here, or give this sort of teaser? Initially I had "86 events by 3 individuals" here, but then we ignore that for a couple paragraphs of context before getting back into it... which seemed weird-->

@@
